---
title: "ID5059_1_190018562"
author: "Sophia"
date: "02/03/2022"
output: html_document
---
Please find committed changes in my github repository <https://github.com/selsiekiely/ID5059_190018562>.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import DataSet

```{r}
vehicles <- read.csv("C:/Users/Sophia/ID5059/vehicles.csv")
head(vehicles)
```

## Testing and Training

We split the data into training and test data using a 80/20 split respectively. Seed is set at last
four digits of student ID number.

```{r}
library(caTools)
set.seed(8562)
split = sample.split(vehicles$price, SplitRatio = 0.8)
training_set = subset(vehicles, split == TRUE)
test_set = subset(vehicles, split == FALSE)
```

We will train on 80% of our data and then test on 20% of the data.

```{r}
library(tidyverse)
ggplot()
```

.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
