---
title: "ID5059_1_190018562"
author: "Sophia"
date: "02/03/2022"
output: html_document
---

Please find committed changes in my github repository <https://github.com/selsiekiely/ID5059_190018562>.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import DataSet containing factors for sales of used cars.

```{r}
vehicles <- read.csv("C:/Users/Sophia/ID5059/vehicles.csv")
head(vehicles)
colnames(vehicles)
```

We provide the following data wrangling;

Remove unnecessary columns such as ‘id’, ’URL,’ region’, ‘region_url’, ‘image_url’, ‘lat’, ‘size’, 'VIN' and ’long’ because these do not contain metric data that can be utilised in price entry predictions even with feature engineering.


```{r}
library(dplyr)
vehicles <- vehicles %>% 
  select(-id, -url, -region, -region_url, -image_url, -lat, -size, -long, -VIN)
```

Even after this removals it is necessary to remove rows that contain too many NAs. If we summarise all the variables we can also locate outliers.

```{r}
summary(vehicles$price)
max(vehicles$price)
n <- length(vehicles$price)
sort(vehicles$price,partial=n-2)[n-2]
summary(vehicles$year)
```


```{r}
#Make all entries numeric
for(i in 1:ncol(vehicles)) {       # for-loop over columns
  vehicles[ , i] <- as.numeric(as.character(vehicles[ , i]))
}

#vehicles_lm <- lm(price ~ year + condition + manufacturer + odometer, data = vehicles, na.action = #na.omit)

#However, this does not work because there are 0 non-NA cases. We need to find an alternative way to #replace the NAs.
#This would be overkill with ALL of the variables. Using summaries for each variable lets cut down to our 4 choices of variant now.

summary(vehicles$price)
plot(vehicles$price)
summary(vehicles)

```

## Testing and Training

We split the data into training and test data using a 80/20 split respectively. Seed is set at last
four digits of student ID number.

```{r}
set.seed(8562)
  
# create an index for separating out test and training data (50% split) 
  
trainInd <- sample(1:nrow(vehicles), round(nrow(vehicles)*0.80))
testResponse <- vehicles[-trainInd , "price"]
```

We will train on 80% of our data and then test on 20% of the data.

```{r}
library(randomForest)
library(ISLR2)
library(tidyverse)
```

```{r}
vehiclesBag <- randomForest(price ~ ., data = vehicles, subset = trainInd, mtry = 12, ntree = 25)

# predict to the test data 
bagPred <- predict(vehiclesBag , newdata = vehicles[-trainInd , ])
  
# our test MSE
mean((bagPred - testResponse)^2)
```
We receive an error because there are missing values in object.

```{r}
Price <- training_set$price
Region <- as.integer(as.factor(training_set$region))
Year <- training_set$year
par(mfrow=c(3,2))
hist(Price)
boxplot(Price, horizontal=TRUE)
hist(Region)
boxplot(Region, horizontal=TRUE)
hist(Year)
boxplot(Year, horizontal=TRUE)
```

Data Wrangle for purposes of removing "NA"'S and fuller elements

```{r}
```